\documentclass[10pt,a4paper]{moderncv}

%=======
% Styles
%=======

% see https://gb.mirrors.cicku.me/ctan/macros/latex/contrib/moderncv/manual/moderncv_userguide.pdf
\moderncvstyle{classic}
\moderncvcolor{grey}

% character encoding
\usepackage{cmap}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[english]{babel}

% adjust the page margins
\usepackage[scale=0.85]{geometry}

% if you want to change the width of the column with the dates
\setlength{\hintscolumnwidth}{6em}
\recomputelengths

%==============
% Personal data
%==============
\name{Oleg}{Efimov}
\title{Platform Engineer}
\phone[mobile]{+44-7435-348-567}
\email{efimovov@gmail.com}
\address{London, UK}
\social[linkedin]{oefimov}
\social[github]{Sannis}
% END{personal data}

\nopagenumbers{}

%========
% Content
%========

\begin{document}

\maketitle

\section{Experience}

\cventry{Jan 2019 -- Present}{Principal Engineer, Backend Platform}{Bumble}{London, UK}{}{
  \begin{itemize}%
    \item Oversaw architectural leadership across media infrastructure, user authentication data storage,\newline{}
          GDPR compliance, and data sovereignty initiatives.
    \item Led the backend and infrastructure effort for ramping up two additional on-premises data centers\newline{}
          and expanding into Google Cloud.
    \item Drove improvements in observability, including standardization of metrics collection and alerting practices across services in the platform and beyond.
    \item Participated in incident triage and response, helping enhance system reliability and postmortem processes.
    \item Mentored engineers across the Backend Platform (about 20 people) and other cross-functional teams, contributing to career growth and engineering quality.
  \end{itemize}
}

\cventry{Jan 2017 -- Dec 2018}{Staff Engineer, Backend Platform}{Badoo}{Moscow, Russia}{}{
  \begin{itemize}%
    \item Joined the Backend Platform team and assumed ownership of the user-generated media infrastructure.
    \item Introduced observability for edge and storage services, enabling detailed latency and throughput analysis.
    \item Refactored storage services to support horizontal scaling and reduce memory usage significantly.
    \item Migrated edge infrastructure from proprietary F5 LTM hardware to an internal solution\newline{}
          based on IPVS and Nginx.
    \item Managed a team of four, fostering collaboration and innovation within Backend Platform.
  \end{itemize}
}

\cventry{Jan 2014 -- Dec 2016}{Lead Engineer, Apps Backend}{Badoo}{Moscow, Russia}{}{
  \begin{itemize}%
    \item Led the integration of advanced filtering and privacy models, improving user experience and safety.
    \item Improved fairness and accuracy of geo-based voting and matching algorithms across global markets.
    \item Developed a WiFi-based user acquisition platform used in partnership-driven marketing campaigns.
    \item Established consistent performance tracking across the product backend, driving operational efficiency.
  \end{itemize}
}

\cventry{Jul 2012 -- Dec 2013}{Senior Engineer, Apps Backend}{Badoo}{Moscow, Russia}{}{
  \begin{itemize}%
    \item Contributed to core features of the matching engine, helping boost user engagement and retention.
    \item Played a key role in launching FriendPath and HotOrNot, significantly expanding the platform’s social\newline{}
          and viral capabilities.
    \item Improved friends network processing performance 10x by integrating the Judy array library,\newline{}
          reducing memory footprint and speeding up graph operations.
  \end{itemize}
}

\cventry{Apr 2012 -- Jun 2012}{PHP Developer}{Mail.ru Group}{Moscow, Russia}{}{
  \begin{itemize}%
    \item Contributed to the successful migration of ICQ’s codebase and infrastructure from Israel and the US\newline{}
          to Russia after the company's acquisition.
    \item Collaborated closely with Site Reliability Engineers on infrastructure setup and deployment coordination.
    \item Managed the planning and execution of data and codebase transfers within a tight one-month timeline.
  \end{itemize}
}

\cventry{Feb 2011 -- Mar 2012}{PHP Developer}{Wikimapia}{Moscow, Russia}{}{
  \begin{itemize}%
    \item Collaborated as one of three backend engineers at Wikimapia, a geographical encyclopedia startup.
    \item Developed region- and city-level portals, enhancing user engagement and accessibility.
    \item Introduced a comprehensive monitoring for 18 production servers, improving system reliability.
  \end{itemize}
}

\section{Education}
\cventry{Sep 2005 -- Jan 2011}{Specialist}{M. V. Lomonosov Moscow State University}{Moscow}{}{}

\section{Languages}
\cvlanguage{Russian}{Native}{}
\cvlanguage{English}{Fluent}{}

\end{document}
